### 2022-02-14 introduction/introduction.tex
more

>>>>

Despite this negative result, the prospect of automatically proving theorems of
first-order logic remained too enticing. In 1960 Davis and Putnam
\cite{dp-1960-dpll} described an algorithm for checking validity of a
first-order formula. As first-order logic is undecidable this algorithm
terminated only on valid formulas. Even though it was efficient enough to prove
only simple formulas, it was an impressive achievement for the time.

A bigger breakthrough happened in 1965 when Robinson introduced a formal system
(calculus) that would shape the future of automatic reasoning --- the resolution
calculus \cite{ar-65-resolution}. Consisting of a single inference rule it was
simple and elegant. It was also \emph{complete}: each theorem could be proven
using this system. Furthermore, it was less explosive that Davis and Putnam's
algorithm since it introduced unification as an inference filter.

Since the introduction of resolution calculus it was improved in many ways.
Strategies and heuristics \cite{lw-65-sos} to curb the explosion of the search
space were introduced, as well as variants of resolution calculus that are less
explosive than the original calculus but still complete .
